---
title: "Reproducible-Research-Week2"
author: "FengSi"
date: "2016-9-5"
output: html_document
---

###Section 1:Loading and preprocessing the data

```{r}
unzip(zipfile="repdata%2Fdata%2Factivity.zip")
dataRaw <- read.csv("activity.csv")
data <- dataRaw[complete.cases(dataRaw),]
```

##Section 2:What is mean total number of steps taken per day?
```{r}
library(ggplot2)
totalSteps <- tapply(data$steps, data$date, FUN=sum, na.rm=TRUE)
qplot(totalSteps, binwidth=1000, xlab="Total number of steps taken per day")
mean(totalSteps, na.rm=TRUE)
median(totalSteps, na.rm=TRUE)
```

##Section 3:What is the average daily activity pattern?
```{r}
library(ggplot2)
averages <- aggregate(x=list(steps=data$steps), by=list(interval=data$interval),
                      FUN=mean, na.rm=TRUE)
ggplot(data=averages, aes(x=interval, y=steps)) +
    geom_line() +
    xlab("5-minute interval") +
    ylab("Average number of steps taken")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
averages[which.max(averages$steps),]
```
##Section 4:Imputing missing values
There are many days/intervals where there are missing values (coded as NA). The presence of missing days may introduce bias into some calculations or summaries of the data.
```{r}
fillValue <- function(steps, interval) {
    filled <- NA
    if (!is.na(steps))
        filled <- c(steps)
    else
        filled <- (averages[averages$interval==interval, "steps"])
    return(filled)
}
filledData <- data
filledData$steps <- mapply(fillValue, filledData$steps, filledData$interval)
```

Histogram of the total number of steps taken each day and calculate the mean and median total number of steps.
```{r}
totalSteps <- tapply(filledData$steps, filledData$date, FUN=sum)
qplot(totalSteps, binwidth=1000, xlab="total number of steps taken each day")
mean(totalSteps)
median(totalSteps)
```

##Section 5:Are there differences in activity patterns between weekdays and weekends?
```{r}
weekday.or.weekend <- function(date) {
    day <- weekdays(date)
    if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
        return("weekday")
    else if (day %in% c("Saturday", "Sunday"))
        return("weekend")
    else
        stop("invalid date")
}
filledData$date <- as.Date(filledData$date)
filledData$day <- sapply(filledData$date, FUN=weekday.or.weekend)
```

Panel plot containing plots of average number of steps taken on weekdays and weekends.
```{r}
averages <- aggregate(steps ~ interval + day, data=filledData, mean)
ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) +
    xlab("5-minute interval") + ylab("Number of steps")
```


